Lexical Richness as a Lens: Exploring the Influence of Social Class on Authors' Writings

### 2024-03-17 paper/paper.qmd
fixing ratios again
fixing spaceeeee
spacingggggggg whyyyyyyy
spacing final
fixing space

```{r}
#| label: tbl-multi-lev-model
#| tbl-cap: Model Summary of Multi-level and Negative Binomial model
#| echo: false
#| warning: false

@@

@tbl-multi-lev-model provides coefficients from a negative binomial regression and a multilevel negative binomial regression, indicating how each author's work differs from the intercept in terms of Corrected Type-Token Ratio (CTTR). 
Hugh Garners shows a negative coefficient (-0.658 in Neg Binom and -1.308 in Multilevel Neg Binom), suggesting his CTTR is significantly lower than the baseline set by the intercept, which is consistent with the shortest average word count observed in the previous analysis. 
Nancy Mitford's coefficient is slightly above zero (0.021 in Neg Binom and 0.152 in Multilevel Neg Binom), indicating her CTTR is almost at the baseline level. This aligns with her position as neither the lowest nor the highest in terms of lexical richness. 
Powell Anthony’s positive coefficient (0.107 in Neg Binom and 0.153 in Multilevel Neg Binom) implies his CTTR is above the baseline, though not as high as David Herbert Lawrence's. 
David Herbert Lawrence does not have a coefficient listed here but is included in the distribution figure below.

@@

Hugh Garners' distribution is broader and notably shifted to the left of the baseline in both models, implying a lower CTTR and greater variability in lexical richness compared to the others. David Herbert Lawrence, while not explicitly compared against a coefficient in the table, is represented in the figure with the broadest distribution. This suggests that his CTTR is highly variable, confirming the previous analysis which indicated his works are both lengthy and diverse in terms of lexical richness.
Overall, the @fig-multi-lev-model-by-author corroborates the numerical findings of @tbl-multi-lev-model, offering a visual confirmation of the differences in lexical richness and variability among the authors. It highlights the significant spread in the lexical diversity of Lawrence's works, as well as the relative consistency observed in the writings of Powell Anthony and Nancy Mitford, with Garners' works showing both a lower mean and a higher dispersion.

@@

```{r}
#| label: fig-cttr-vs-wordcount
#| fig-cap: Comparison Between CTTR and Word Count by Authors
#| echo: false

>>>>

```{r}
#| label: tbl-multi-lev-model
#| tbl-cap: Model Summary of Multi-level and Negative Binomial model
#| tbl.pos: "H"
#| echo: false
#| warning: false

@@

@tbl-multi-lev-model provides coefficients from a negative binomial regression and a multilevel negative binomial regression, indicating how each author's work differs from the intercept in terms of Corrected Type-Token Ratio (CTTR). 
Hugh Garners shows a negative coefficient (-0.658 in Neg Binom and -1.308 in Multilevel Neg Binom), suggesting his CTTR is significantly lower than the baseline set by the intercept, which is consistent with the shortest average word count observed in the previous analysis.

Nancy Mitford's coefficient is slightly above zero (0.021 in Neg Binom and 0.152 in Multilevel Neg Binom), indicating her CTTR is almost at the baseline level. This aligns with her position as neither the lowest nor the highest in terms of lexical richness. 
Powell Anthony’s positive coefficient (0.107 in Neg Binom and 0.153 in Multilevel Neg Binom) implies his CTTR is above the baseline, though not as high as David Herbert Lawrence's.
David Herbert Lawrence does not have a coefficient listed here but is included in the distribution figure below.

@@

Hugh Garners' distribution is broader and notably shifted to the left of the baseline in both models, implying a lower CTTR and greater variability in lexical richness compared to the others. David Herbert Lawrence, while not explicitly compared against a coefficient in the table, is represented in the figure with the broadest distribution. This suggests that his CTTR is highly variable, confirming the previous analysis which indicated his works are both lengthy and diverse in terms of lexical richness.

Overall, the @fig-multi-lev-model-by-author corroborates the numerical findings of @tbl-multi-lev-model, offering a visual confirmation of the differences in lexical richness and variability among the authors. It highlights the significant spread in the lexical diversity of Lawrence's works, as well as the relative consistency observed in the writings of Powell Anthony and Nancy Mitford, with Garners' works showing both a lower mean and a higher dispersion.

@@

```{r}
#| label: fig-cttr-vs-wordcount
#| fig-cap: Comparison Between CTTR and Word Count by Authors
#| fig.pos: "H"
#| echo: false
